X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on a conventional source

### 2014-03-04 hedpc.tex
arrow in figure 2, comparison of AR

\section*{Results}
We introduce a method for phase contrast imaging which works on
conventional X-ray sources, covers the entire diagnostic X-ray energy range
and is compatible with compact imaging arrangements. The approach is based
on Talbot-Lau interferometry~\cite{Pfeiffer2006} and employs an edge-on
illumination approach for the grating design and arrangement. Our solution
removes one of the major hurdles which prevented grating interferometry from
being
applied at high energies so far, namely the fabrication of
gratings with high aspect ratios. The aspect ratio, given by
\begin{equation}
    \text{R} = \frac{2h}{p},
\end{equation}
where $p$ is the
grating period and $h$ the  structure height, is limited by the
fabrication process, usually photolithography~\cite{David2002} or X-ray
lithography~\cite{Mohr2012} since grating structures tend to collapse or deform
(e.g.\ due to capillary forces) if the aspect ratio is too high. For a given
setup length these parameters depend on the target energy $E$ according to
$p \propto 1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$
an aspect ratio for the absorption grating around $\textnormal{R}=30$ is
sufficient, it would
have to be at least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover,
when using a broad spectrum, photons above the design energy should also be
efficiently blocked by the gratings, thus requiring even higher aspect
ratios. The largest aspect ratios achieved by current fabrication
techniques~\cite{David2007,Kenntner2010} are around 60.

>>>>

\section*{Results}
We introduce a method for phase contrast imaging which works on
conventional X-ray sources, covers the entire diagnostic X-ray energy range
and is compatible with compact imaging arrangements. The approach is based
on Talbot-Lau interferometry~\cite{Pfeiffer2006} and employs an edge-on
illumination approach for the grating design and arrangement. Our solution
removes one of the major hurdles which prevented grating interferometry from
being
applied at high energies so far, namely the fabrication of
gratings with high aspect ratios. The aspect ratio, given by
\begin{equation}
    \text{R} = \frac{2h}{p},
\end{equation}
where $p$ is the
grating period and $h$ the  structure height, is limited by the
fabrication process, usually photolithography~\cite{David2002} or X-ray
lithography~\cite{Mohr2012} since grating structures tend to collapse or deform
(e.g.\ due to capillary forces) if the aspect ratio is too high. For a given
setup length these parameters depend on the target energy $E$ according to
$p \propto 1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$
an aspect ratio for the absorption grating around $\textnormal{R}=30$ is
sufficient, it would
have to be at least $\num{128}$ for $E=\SI{100}{\kilo\electronvolt}$. This
is the case for the synchrotron interferometer with a design energy
of~\SI{82}{\kilo\eV}~\cite{Willner2013}, where an aspect ratio of \num{21}
is reported with a transmission of \SI{20}{\percent}. The aspect ratio in
the present experiment reaches \num{143}. Moreover,
when using a broad spectrum, photons above the design energy should also be
efficiently blocked by the gratings, thus requiring even higher aspect
ratios. The largest aspect ratios achieved by current fabrication
techniques~\cite{David2007,Kenntner2010} are around 60.
